\begin{axdef}
  maxGoalkeeperSubs: \nat \\
  maxPlayerSubs: \nat 
\where
  maxGoalkeeperSubs = 1\\
  maxPlayerSubs = 2
\end{axdef}

\begin{axdef}
  Player: \power  \nat 
\where
  Player = 1 \upto 99
\end{axdef}

\begin{schema}{RefBook}
  team: \finset  Player\\
  players: \finset  Player\\
  substitutes: \finset  Player\\
  redcards: \finset  Player\\
  goalkeeper: \finset  Player\\
  goalkeeperSubs: \nat \\
  playerSubs: \nat \\
 % out: \finset Player\\
\where
  team = players \cup  substitutes \\%\cup redcards\\
  \# team \leq  16\\
 %  \# players \geq 7\\
   \# players \leq 11\\
 % 7 \leq \# players \leq 11\\
  goalkeeper \subseteq  players\\
  goalkeeperSubs \leq  maxGoalkeeperSubs\\
  playerSubs \leq  maxPlayerSubs
\end{schema}

\begin{schema}{Init}
 RefBook'
\where
%team' = 1 \upto 16\\
players' = 1 \upto 11\\
substitutes' = 12 \upto 16\\
redcards' = \emptyset\\
goalkeeper' = \{1\}\\
goalkeeperSubs' = 0\\
playerSubs' = 0\\
%out' = \emptyset\\
\end{schema}

\begin{schema}{Redcard\_Player}
  \Delta RefBook\\
   p?: Player
\where
   p? \in team\\
  \#team \leq 16\\
  team' = team \setminus \{p? \}\\ 
   redcards' = redcards \cup \{p? \}\\
 % players  = 1 \upto 6\\
 % substitutes' = 12 \upto 16\\
   players' = players \setminus \{p? \}\\
   substitutes' = substitutes \setminus \{p? \}\\ 
   goalkeeper'=goalkeeper \setminus \{p? \}\\
   goalkeeperSubs' = goalkeeperSubs\\
   playerSubs' = playerSubs\\
 %  out' = \emptyset\\
\end{schema}

\begin{schema}{Change\_Goalkeeper}
  \Delta RefBook\\
   new?: Player
\where
   new? \in (players \cup goalkeeper) \\
   team' = team \\
   redcards' = redcards \\
   players' = players \\
   substitutes' = substitutes \\
   goalkeeper' = \{ new? \}\\
   goalkeeperSubs' = goalkeeperSubs\\
   playerSubs' = playerSubs\\
   %out' = \emptyset\\
\end{schema}

\begin{schema}{Substitute\_Player}
  \Delta RefBook\\
   new?: Player \\
   old?: Player
\where
   new? \in substitutes\\
   old? \in players \\
   old? \notin goalkeeper\\
   team' = team \setminus \{old? \}\\
   redcards' = redcards\\
   players' = players \setminus \{old? \} \cup \{new? \}\\
   substitutes' = substitutes \setminus \{new? \}\\ 
   goalkeeper' = goalkeeper\\
   playerSubs < maxPlayerSubs\\
   goalkeeperSubs' = goalkeeperSubs\\
   playerSubs' =  playerSubs + 1\\
 % out' = out \cup \{old? \}\\
\end{schema} 

\begin{schema}{Substitute\_Goalkeeper}
  \Delta RefBook\\
   new?: Player \\
   old?: Player
\where
  new? \in substitutes \\
  old? \in players \\
  old? \in goalkeeper \\
    team' = team \setminus \{old? \}\\
    redcards' = redcards\\
   players' = players \setminus \{old? \} \\\cup \{new? \}\\
   substitutes' = substitutes \setminus \{old? \}\\ 
 %  substitutes' = substitutes \\
   goalkeeper' = goalkeeper \setminus \{old? \} \cup \{new? \} \\
   goalkeeperSubs < maxGoalkeeperSubs\\
   goalkeeperSubs' = goalkeeperSubs + 1   \\
   playerSubs' =  playerSubs \\
 % out' = out \cup \{old? \}\\
\end{schema} 

